---
title: "CapstoneProjectPrediction"
author: "Jeff Sternin"
date: "April 1, 2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(readtext)
require(quanteda)
require(stringi)
require(ggplot2)
options(warn = -1)
MB <- (1024) * (1024)
```




## 1.1 Function , helpers: result  and ngram dfm

```{r makeresult, echo = TRUE, include = TRUE}
result <- function(obj) {
  mem <- object.size(obj)/MB  
  obj_name <- class(obj)[1]
  print(sprintf("%s size: %5.1f Mb",obj_name,mem))
}
```


```{r makengram, echo = TRUE, include = TRUE}
dfm_ngram <- function(ngrm,tail=10)  {
  print(sprintf("building dfms%d....",ngrm))
  tokc <- tokens_ngrams(toks,n=ngrm,concatenator=" ")  ## ok use _
  result(tokc)
  dfm_res <-  tokc %>% dfm() %>% dfm_trim(min_count=tail)
  result(dfm_res)
  rm(tokc)
  dfm_res
}
```


## 2. Processing1 : corpus
```{r make_corpus, echo = TRUE, include = TRUE}
wd <- normalizePath(getwd(),winslash='\\',mustWork = NA)
localFiles <- paste0(wd,"\\..\\Coursera-SwiftKey\\final\\en_US\\")
system.time(all_data <- readtext(paste0(localFiles,"*.txt"),text_field = "texts"))
system.time(all_data$text <- iconv(all_data$text, "latin1", "ASCII", sub="")) ## remove strange chars!!!!
system.time(corp <- corpus(all_data))
rm(all_data)
saveRDS(corp,file="corp.rds")
result(corp)

```



## 2.0 toks with stop words
```{r make_toks_full, echo = TRUE, include = TRUE}
system.time(toks <- corp %>% tokens(remove_punct=TRUE) %>% tokens_tolower())
##rm(corp)
saveRDS(toks,file="toksfull.rds")
result(toks)
```
## 2.1 dfms1 with stop words (tail=15 - no less than 15 repetitions)
```{r make_dmfs2, echo = TRUE, include = TRUE}
system.time(dfms1 <- dfm_ngram(1,2)) ## 23MB
saveRDS(dfms1,file="dfms1.rds")
```


## 2.2 dfms2 with stop words (tail=15 - no less than 15 repetitions)
```{r make_dmfs2, echo = TRUE, include = TRUE}
system.time(dfms2 <- dfm_ngram(2,15)) ## 39MB
saveRDS(dfms2,file="dfms2.rds")
```

## 2.3 dfms3 with stop words (trigrams & tail=10)
```{r make_dmfs3, echo = TRUE, include = TRUE}
system.time(dfms3 <- dfm_ngram(3,10)) ## 58MB
saveRDS(dfms3,file="dfms3.rds")
```
## 2.3 dfms4 with stop words (4-grams & tail=7)
```{r make_dmfs4, echo = TRUE, include = TRUE}
system.time(dfms4 <- dfm_ngram(4,7))  ## 40MB
saveRDS(dfms4,file="dfms4.rds")
```
## 2.4 dfms5 with stop words (5-grams & tail=5)
```{r make_dmfs5, echo = TRUE, include = TRUE}
system.time(dfms5 <- dfm_ngram(5,5)) ## 21MB
saveRDS(dfms5,file="dfms5.rds")
```

## 2.5 dfms6 with stop words (6-grams & tail=5)
```{r make_dmfs6, echo = TRUE, include = TRUE}
system.time(dfms6 <- dfm_ngram(6,3))
saveRDS(dfms6,file="dfms6.rds")
```


```{r get_memory, include=FALSE}
#print(object.size(x=lapply(ls(pattern="^dfm[1-3]"), get)), units="Mb")
#print(object.size(x=lapply(ls(pattern="^dfm[4-6]"), get)), units="Mb")
#print(object.size(x=lapply(ls(pattern="^dfms[2-3]"), get)), units="Mb")
nfeat(dfms2);nfeat(dfms3);
print(object.size(x=lapply(ls(pattern="^dfms[4-5"), get)), units="Mb")
nfeat(dfms4);nfeat(dfms5);
print(object.size(x=lapply(ls(pattern="^dfms6"), get)), units="Mb")
nfeat(dfms6)
```

```{r clean tokens, echo = TRUE, include = TRUE}
print("Removing tokens with stop words we make dfm2, and dfm3")
rm(toks)
```

## 6. Processing - creating : toks

```{r make_toks, echo = TRUE, include = TRUE}
system.time(toks <- corp %>% 
            tokens(remove_punct=TRUE) %>% 
            tokens_tolower() %>%
            tokens_select(stopwords('en'), selection = 'remove'))
rm(corp)
saveRDS(toks,file="toks.rds")
result(toks)
```

## 7.Processing2 - creating : dfm1  

```{r make_dmf1, echo = TRUE, include = TRUE}
system.time(dfm1 <- toks %>% dfm() %>% dfm_trim(min_count=10))
saveRDS(dfm1,file="dfm1.rds")
result(dfm1)
```

## 8.Processing3 - creating : dfm2,dfm3,dfm4,dfm5,dfm6

```{r make_dmf2, echo = TRUE, include = TRUE}
system.time(dfm2 <- dfm_ngram(2))
saveRDS(dfm2,file="dfm2.rds")
```


```{r make_dmf3, echo = TRUE, include = TRUE}
system.time(dfm3 <- dfm_ngram(3,3))
saveRDS(dfm3,file="dfm3.rds")
```


```{r make_dmf4, echo = TRUE, include = TRUE}
system.time(dfm4 <- dfm_ngram(4,2))
saveRDS(dfm4,file="dfm4.rds")
```

```{r make_dmf5, echo = TRUE, include = TRUE}
system.time(dfm5 <- dfm_ngram(5,2))
saveRDS(dfm5,file="dfm5.rds")
```


##```{r make_dmf6, echo = TRUE, include = TRUE}
####system.time(dfm6 <- dfm_ngram(6))
```


## Processing 3